Consumer extinctions constrain phenotypic evolution in the resulting food web

### 2019-09-13 analyses/reproduce_analyses.Rmd
updated file and changed figures labels in main text to "removal" instead of "extinction".

```{r Table of differences in food web coefficients, include=FALSE}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  #select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces for gall midges between food-web treatments.")
```

@@

```{r Curvature}
# Get mean estimates for directional selection gradients
foodweb_original_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Original", term == "sc.Diam")$mean
foodweb_original_mean_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Original", term == "sc.log.Clutch")$mean
foodweb_original_mean_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Original", term == "sc.sqrt.Pref")$mean

@@

# Calculate curvatures for original food web
foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

@@

```{r Table of food web curvatures, include=FALSE}
tidy_foodweb_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
```

```{r Table of differences in curvatures between food-web treatments, include=FALSE}
tidy_foodweb_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
```

@@

```{r Tidy up long-term selection gradients}
# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_long_grads <- bind_cols(foodweb_original_raw_gradients, foodweb_long_extinction_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Curvature long-term, include=FALSE}
# Get mean estimates for directional selection gradients
# Note we already have the mean estimates for the original food web

@@

```{r Table of differences in long-term curvatures between food-web treatments, include=FALSE}
tidy_foodweb_long_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in long-term curvatures on gall traits between food-web treatment.")
```

@@

@@

# Gall size 
AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Mean larval survival") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
  coord_cartesian(ylim=c(0.07,1))

@@

# Make plots
AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
                       AF_uni_Pref + theme(legend.position = "none", 
                                           axis.title.y = element_blank()) + xlab("Preference (SDs)"),
                      AF_uni_Clutch + theme(legend.position = "none",
                                             axis.title.y = element_blank()), 
                       labels = "AUTO", nrow = 1, align='hv')

@@

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Original","Extinction")), type="response", re.form=~0)
names(breaks) <- c("Original","Extinction")

@@

# Size x Clutch
RF_Diam.Clutch$absolute_fitness <- RF_Diam.Clutch$absolute_fitness %>%
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))

AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
RF_Diam.Pref$absolute_fitness <- RF_Diam.Pref$absolute_fitness %>% 
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))

AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Clutch x Preference
RF_Clutch.Pref$absolute_fitness <- RF_Clutch.Pref$absolute_fitness %>%
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))

AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Oviposition preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

>>>>

```{r Table of differences in food web coefficients}
tidy_foodweb_alphas %>%
  filter(type == "Diff") %>%
  #select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
 knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces for gall midges between food-web treatments.")
```

@@

```{r Curvature, echo=TRUE}
# Get mean estimates for directional selection gradients
foodweb_original_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Original", term == "sc.Diam")$mean
foodweb_original_mean_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Original", term == "sc.log.Clutch")$mean
foodweb_original_mean_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Original", term == "sc.sqrt.Pref")$mean

@@

# Calculate curvatures for original food web
foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

@@

```{r Table of food web curvatures}
tidy_foodweb_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
```

```{r Table of differences in curvatures between food-web treatments}
tidy_foodweb_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
```

@@

```{r Tidy up long-term selection gradients, echo=TRUE}
# Calculate differences between food-web treatments, then estimate means and confidence intervals
foodweb_long_grads <- bind_cols(foodweb_original_raw_gradients, foodweb_long_extinction_raw_gradients) %>%
  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

@@

```{r Curvature long-term, echo=TRUE}
# Get mean estimates for directional selection gradients
# Note we already have the mean estimates for the original food web

@@

```{r Table of differences in long-term curvatures between food-web treatments}
tidy_foodweb_long_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in long-term curvatures on gall traits between food-web treatment.")
```

@@

```{r Curvature egg vs. larval, echo=TRUE}
# Get mean estimates for directional selection gradients
egglarval_original_mean_sc.Diam <- filter(tidy_egglarval_grads, type == "Original", term == "sc.Diam")$mean
egglarval_original_mean_sc.log.Clutch <- filter(tidy_egglarval_grads, type == "Original", term == "sc.log.Clutch")$mean
egglarval_original_mean_sc.sqrt.Pref <- filter(tidy_egglarval_grads, type == "Original", term == "sc.sqrt.Pref")$mean

egglarval_extinction_mean_sc.Diam <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.Diam")$mean
egglarval_extinction_mean_sc.log.Clutch <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.log.Clutch")$mean
egglarval_extinction_mean_sc.sqrt.Pref <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean

# Calculate curvatures for original food web
egglarval_original_raw_curvs <- egglarval_original_raw_gradients %>%
  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - egglarval_original_mean_sc.log.Clutch*egglarval_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - egglarval_original_mean_sc.sqrt.Pref*egglarval_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - egglarval_original_mean_sc.log.Clutch*egglarval_original_mean_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)

# Calculate curvatures for extinction food web
egglarval_extinction_raw_curvs <- egglarval_extinction_raw_gradients %>%
  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - egglarval_extinction_mean_sc.log.Clutch*egglarval_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - egglarval_extinction_mean_sc.sqrt.Pref*egglarval_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - egglarval_extinction_mean_sc.log.Clutch*egglarval_extinction_mean_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)

# Calculate differences between food-web treatments, then estimate means and confidence intervals
egglarval_curvs <- bind_cols(egglarval_original_raw_curvs, egglarval_extinction_raw_curvs) %>%
  mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
         `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
         `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
         `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
         `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
         `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`) %>%
  summarise_all(funs(mean, conf.high, conf.low))

# Tidy up estimates
tidy_egglarval_curvs <- egglarval_curvs %>%
  t() %>%
  as.data.frame() %>%
  transmute(rows = rownames(.), value=V1) %>%
  separate(col = rows, into = c("term","estimate"), sep="_") %>%
  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
  separate(col = type, into = c("extra","type"), sep = 7) %>%
  select(type, term, estimate, value) %>%
  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
  spread(estimate, value) %>%
  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
```

```{r Table of curvatures for egg and larval parasitoids}
tidy_egglarval_curvs %>%
  filter(type != "Diff") %>%
  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of curvatures on gall traits due to egg and larval parasitoids.")
```

```{r Table of differences in curvatures between egg and larval parasitoids}
tidy_egglarval_curvs %>%
  filter(type == "Diff") %>%
  select(term, mean, conf.low, conf.high, P_cutoff) %>%
  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
  knitr::kable(., caption = "Table of differences in curvatures on gall traits between egg and larval parasitoids.")
```

@@

# Gall size 
AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal"))) %>% 
  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Chamber diameter (SDs)") +
  ylab("Mean larval survival") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
  coord_cartesian(ylim=c(0.07,1))

@@

# Make plots
AF_uni_plots <- plot_grid(AF_uni_Clutch + theme(legend.position = "none"),
                          AF_uni_Pref + theme(legend.position = "none", 
                                           axis.title.y = element_blank()) + xlab("Preference (SDs)"),
                          AF_uni_Diam + theme(legend.position = "none",
                                             axis.title.y = element_blank()), 
                       labels = "AUTO", nrow = 1, align='hv')

@@

# Set contour breaks
breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Original","Extinction")), type="response", re.form=~0)
names(breaks) <- c("Original","Removal")

@@

# Size x Clutch
RF_Diam.Clutch$absolute_fitness <- RF_Diam.Clutch$absolute_fitness %>%
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))

AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Size x Preference
RF_Diam.Pref$absolute_fitness <- RF_Diam.Pref$absolute_fitness %>% 
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))

AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Chamber diameter (SDs)") +
  ylab("Oviposition preference (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

# Clutch x Preference
RF_Clutch.Pref$absolute_fitness <- RF_Clutch.Pref$absolute_fitness %>%
  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))

AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
  filter(Foodweb == "Original") %>%
  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
  geom_raster(aes(fill=average)) +
  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
  facet_wrap(~Foodweb) + # , labeller = labeller_2D
  xlab("Oviposition preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
  theme(strip.background = element_blank(),
        strip.text.x=element_text(margin=margin(b=4)))

@@

```{r Curvatures in matrix form, echo=TRUE}
## Original

# Get curvatures from original food web
original_curvs_df <- tidy_foodweb_curvs %>%
  filter(type=="Original") %>%
  select(term, mean, low=conf.low, high=conf.high)

rownames(original_curvs_df) <- original_curvs_df$term

## Extinction

# Get curvatures from extinction food web
extinction_curvs_df <- tidy_foodweb_curvs %>%
  filter(type=="Extinction") %>%
  select(term, mean, low=conf.low, high=conf.high)

rownames(extinction_curvs_df) <- extinction_curvs_df$term

## Difference
difference_curvs_df <- tidy_foodweb_curvs %>%
  filter(type=="Diff") %>%
  select(term, mean, low=conf.low, high=conf.high)

rownames(difference_curvs_df) <- difference_curvs_df$term
```
